Untwisting the Tetrahelix (v0.4)

### 2017-02-12 doc/TetrahelixUntwist.tex
light working

\begin{align*}
r_{\lambda}  &=  \lvert \lambda \rvert (\frac{3 \sqrt{3}}{10}  - \sqrt{\frac{8}{27}}) + \sqrt{\frac{8}{27}}  \\
d_{\lambda} &=   \lvert \lambda \rvert (3 \sqrt{10} - 1) + 1 \\
\phi_{\lambda} &=  \lambda \rho_{bc}  + 0
\end{align*}
to create a formula that generates a continuum of tetrahedral structures:

\[
H_{continuum}(n,c,\lambda) =
\left [
  \begin{tabular}{c}
   $ r_{\lambda} \cos(\phi_{\lambda} \kappa + c 2 \pi /3) $\\
   $ r_{\lambda}  \sin(\phi_{\lambda} \kappa + c 2 \pi /3) $\\
   $ d_{\lambda} \kappa $
  \end{tabular}
  \right ],
\text{where:}
  \begin{tabular}{c}
    $\kappa = n + c/3$ \\
    $ \phi_{\lambda} =  \lambda \rho_{bc}  + 0 $\\
    $\rho_{bc} = (3 \theta - 2 \pi)$ \\
   $ \theta = \arccos(-2/3) $
  \end{tabular}      
\]
A value of $\lambda = 0$ generates the equitetrabeam, and $\lambda = 1$ generates the Boerdijk--Coxeter helix, and every
value $\lambda \in [-1,1]$ generates an attractive structure which if physically realized is an inherently rigid structure
with member lengths of no greater disparity than $16\%$.
In the sense of structural engineering, it would be a relatively strong space frame.

@@

>>>>

\begin{align*}
r_{\lambda}  &=  \lvert \lambda \rvert \cdot (\frac{3 \sqrt{3}}{10}  - \sqrt{\frac{8}{27}}) + \sqrt{\frac{8}{27}}  \\
d_{\lambda} &=   \lvert \lambda \rvert \cdot (3 \sqrt{10} - 1) + 1 \\
\phi_{\lambda} &=  \lambda \cdot \rho_{bc}  + 0
\end{align*}
to create a formula that generates a continuum of tetrahedral structures:

\[
H_{continuum}(n,c,\lambda) =
\left [
  \begin{tabular}{c}
   $ r_{\lambda} \cos(\phi_{\lambda} \kappa + c 2 \pi /3) $\\
   $ r_{\lambda}  \sin(\phi_{\lambda} \kappa + c 2 \pi /3) $\\
   $ d_{\lambda} \kappa $
  \end{tabular}
  \right ],
\text{where:}
  \begin{tabular}{c}
    $\kappa = n + c/3$ \\
    $ \phi_{\lambda} =  \lambda \rho_{bc}  + 0 $\\
    $\rho_{bc} = (3 \theta - 2 \pi)$ \\
   $ \theta = \arccos(-2/3) $
  \end{tabular}      
\]
A value of $\lambda = 0$ generates the equitetrabeam, and $\lambda = 1$ generates the Boerdijk--Coxeter helix, and every
value $\lambda \in [-1,1]$ generates an attractive structure which if physically realized is an inherently rigid structure
with member lengths of no greater disparity than $16\%$.
In the sense of structural engineering, it would be a relatively strong space frame. When $\lvert \lambda \rvert > 1$, tetrahelices
are still produced, but as $\lvert \lambda \rvert >> 2$ these tetrahelices probably cease to be interesting to mechanical engineers,
because their ability to withstand axial forces seem to diminish significantly.

@@

Note: Need to understand how pitch is computed from negative lambda values.
